---
title: "Lab 07"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE,
                      message = FALSE, warning = FALSE, comment = NA,
                      fig.width = 9, fig.height = 6)
```

## Introduction

The [Open Movie Database](http://www.omdbapi.com) provides an API to obtain 
movie information. Users can access information such as the plot, year, genre, 
runtime, etc. about a specific movie. Movies can be queried with a valid IMDb 
ID or title.

To get started, create a free account to get an API key at 
http://www.omdbapi.com/apikey.aspx. You'll be able to make 1,000 requests
per day.

## Packages

```{r}
library(tidyverse)
library(jsonlite)
library(rvest)
```

## The Shawshank Redemption

According to IMDB (https://www.imdb.com/chart/top/), the top ranked movie is
The Shawshank Redemption. Use the OMDb API to query the full plot for this
movie. Don't forget to include your API key in the query string.

```{r}

```

Redo your above query, but this time return the data in XML format. You'll need 
to use `rvest` functions to extract the plot. Before you try an parse it,
view the result in your browser by pasting in the URL.

```{r}

```

## Movie search

Perform a search for movies that contain "saw" in the title. How many total
results exist? Coerce those results to a data frame.


## API wrapper

Create an R function that will allow users to easily query movies using the 
API by ID or title. Allow users to use the API parameters `i`, `t`, `plot`,
`r`, and `apikey`. However, you should provide more meaningful names for these
as arguments in your R function; put checks in place to handle bad values. 
For example, according to the API documentation: both "i" and "t" are optional 
at least one argument is required. Your R function should account for this 
requirement.

Once you have your R function written, test it out with a few examples.